Food-web structure, stochasticity and response diversity drive temporal stability in complex communities

### 2023-10-13 _targets.Rmd
Begin to update manuscript figures

```{r}
cols <- c("Community stability" = "black", "Asynchrony" = "blue", "Population stability" = "darkgreen")
alpha <- c("Community stability" = 1, "Asynchrony" = .3, "Population stability" = .3)

p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      y = predictor,
      x = effect,
      color = response,
      alpha = response,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  scale_colour_manual(values = cols) +
  scale_alpha_manual(values = alpha) +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  #facet_grid(cols = vars(response)) +
  labs(
    x = "Total standardised effect",
    color = "Stability component",
    alpha = "Stability component"
    ) +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.justification = "right"
  )
ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = p_sem_tot_stab,
  path = here::here("report", "figures"),
  scale = 1.8,
  dpi = 400,
  width = 80,
  height = 80 * 1.1,
  units = "mm")
```

>>>>

```{r}
library(ggbreak)
cols <- c("Community stability" = "black", "Asynchrony" = "blue", "Population stability" = "darkgreen")
alpha <- c("Community stability" = 1, "Asynchrony" = .3, "Population stability" = .3)
p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      y = predictor,
      x = effect,
      color = response,
      alpha = response,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  scale_colour_manual(values = cols) +
  scale_alpha_manual(values = alpha) +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  #facet_grid(cols = vars(response)) +
  labs(
    x = "Total standardised effect",
    color = "Stability component",
    alpha = "Stability component"
    ) +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    #legend.justification = "right",
    legend.position = "bottom"
  ) +
  scale_x_break(c(-0.3, -0.6))
p_sem_tot_stab_leg <- plot_grid(
  print(p_sem_tot_stab + theme(legend.position = "none")),
  get_legend(p_sem_tot_stab),
  nrow = 2,
  rel_heights = c(1, .05)
)
ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = print(p_sem_tot_stab_leg),
  path = here::here("report", "figures"),
  scale = 1.8,
  dpi = 400,
  width = 80,
  height = 80 * .7,
  units = "mm")
```

### 2023-10-13 paper/manuscript.Rmd
Begin to update manuscript figures

```{r, results = FALSE}

sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM", "semEff", "ggcorrplot", "kableExtra"), require, character.only = TRUE)

@@

```{r}
sem_cap <- paste0("Structural equation model. Only standardized coefficients
  whose absolute values are superior to 0.1 are displayed. [To complete with the links from initial structure]")
```

```{r sem, fig.cap=sem_cap}
knitr::include_graphics(here("report", "figures", "sem_stab2.pdf"))
```

```{r}
tar_load(sem_eff_tab)

get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct") {
  mask <- sem_eff_tab$response == y & sem_eff_tab$predictor == x &
    sem_eff_tab$effect_type == effect_type
  round(sem_eff_tab[mask, ]$effect, d)
}

@@

```{r}
semtot_cap <- "Total effect of food-web structure and stressors on community
stability, asynchony, and population stability. The total effects were derived
from the structural equation model."
```

```{r semtot, fig.cap = semtot_cap}
tar_read(p_sem_tot_stab)
```

>>>>

```{r, results = FALSE}
sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM", "semEff", "ggcorrplot", "kableExtra"), require, character.only = TRUE)

@@

```{r}
sem_cap <- paste0(
  "Structural Equation Model linking initial model parameters to resulting
  temporal stability of biomass. Arrows display positive (continuous) and
  negative (dashed) standardised effects. Initial parameters were initial
  species richness, initial connectance, Prey-Predator Mass Ration (PPMR), hill
  exponent, variance of stochastic mortality rates (Env. stochasticity), and
  cross-correlation among species mortality rates (Env. correlation). We only
  displayed standardised coefficients whose absolute values are superior to 0.1
  are displayed. SEM containing containing further partition of Statistical
  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
```

```{r sem, fig.cap=sem_cap}
knitr::include_graphics(here("report", "figures", "sem_stab_simplified.pdf"))
```

```{r}
#TODO: change most of it for simplified SEM
tar_load(c(sem_eff_tab, sem_simplified_eff_tab))

get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct", tab = sem_eff_tab) {
  mask <- tab$response == y & tab$predictor == x &
    tab$effect_type == effect_type
  round(tab[mask, ]$effect, d)
}

@@

```{r}
semtot_cap <- "Total effect of food-web structure on community stability,
asynchony, and population stability. The total effects were derived from the
structural equation model."
```

```{r semtot, fig.cap = semtot_cap}
knitr::include_graphics(here::here("report", "figures", "p_sem_tot_stab.png"))
```
